Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-04 draft/accordionComplexSurfaces.tex
reverse problem merge

% theorems
\newtheorem{theorem}{Theorem}[]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

@@

\begin{definition}
\label{def:curveOfAWalk}
Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}} \ldots$ be a (possibly infinite) walk on~$\bar Q$. 
Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
\end{definition}

@@

\begin{proposition}
\label{prop:walks=arcs}
The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface(\bar Q)$.
\end{proposition}

@@

>>>>

% theorems
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem*{theorem*}{Theorem}%[section]

@@

\begin{definition}
\label{def:curveOfAWalk}
Let~$\omega = \ldots \alpha_{i-1}^{\varepsilon_{i-1}}\alpha_{i}^{\varepsilon_i}\alpha_{i+1}^{\varepsilon_{i+1}}$ be a (possibly infinite) walk on~$\bar Q$. 
Define the curve~$\curveof(\omega)$ to be the concatenation of the curves~$\curveof(\alpha_i{\varepsilon_{i}})$ of Definition \ref{def:curveOfAnArrow}.
\end{definition}

@@

\begin{proposition}
\label{lem:walks=arcs}
The maps~$\curveof(-)$ and~$\walk(-)$ induce mutually inverse bijections between the set of undirected walks on~$\bar Q$ and the set of~$\dissection_{\bar Q}$-accordions on~$\surface(\bar Q)$.
\end{proposition}

@@

\vincent{Orient the flip graph. Connection to the lattice of torsion classes?}
